### 2022-04-07 README.Rmd
updating README

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations in the Upper Salmon River, Idaho"
Authors <- "Ackerman, Michael W., Nicholas J. Porter, Kevin E. See, Michael S. Hall, Tara E. Blackman, and Richard A. Carmichael, and Michael W. Ackerman"
yr <- 2022
Journal <- "Transactions of the American Fisheries Society"

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BiomarkABS/DeadwaterPaper/main?urlpath=rstudio)

@@

Our pre-print is online here:

> `r Authors` (`r yr`). _`r Title`_. `r Journal`, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Northern Pikeminnow Abundance in Deadwater Slough, Salmon River, Idaho, and Potential Impacts to Local Chinook Salmon Populations"
Authors <- "Ackerman, Michael W., Nicholas J. Porter, Kevin E. See, Tara E. Blackman, Michael S. Hall, and Richard A. Carmichael"
yr <- 2022
Journal <- "Transactions of the American Fisheries Society"

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/mackerman44/DeadwaterPaper/main?urlpath=rstudio)

@@
